---
title: Age of Empires 2 Civilisation Performance Statistics
date: "`r format(Sys.time(), '%d %b %Y')`"
params:
    type: NULL
output:
    html_document:
        theme: cerulean
        toc: true
        toc_depth: 3
        css: [www/jquery-ui.css, www/jquery-ui.structure.css, www/styles.css, www/jquery-ui.theme.css]
        includes:
            in_header: www/header.html
editor_options: 
  chunk_output_type: console
---


```{r, setup, echo = FALSE, results = FALSE, message = FALSE}
devtools::load_all()
library(dplyr)
library(ggplot2)
library(scales)
library(tidyr)
library(lubridate)


knitr::opts_chunk$set(
    echo = FALSE,
    collapse = TRUE,
    message = FALSE,
    warning = FALSE,
    comment = "#>",
    fig.retina = 2, # Control using dpi
    fig.width = 9,
    fig.height = 9 * 5 / 8,
    out.height = "500px",
    out.width = "800px",
    fig.pos = "t",  # pdf mode
    fig.align = "center",
    dpi = if (knitr::is_latex_output()) 72 else 300,
    out.width = "100%",
    dev = "svg",
    dev.args = list(png = list(type = "cairo-png")),
    optipng = "-o1 -quiet"
)


knitr::opts_template$set(square = list(
    fig.width = 9,
    fig.height = 9,
    out.height = "700px",
    out.width = "700px"
))




opts <- get_opts(params$type)

# opts <- get_opts("rm_solo_any")


players <- readRDS("./data/ad_players.Rds")
pre_matchmeta <- readRDS("./data/ad_matchmeta.Rds")

matchmeta <- pre_matchmeta %>%
    filter(
        start_dt >= opts$lower_dt,
        rating_min >= opts$lower_elo,
        leaderboard_name == opts$leaderboard
    )

if (opts$mapclass != "Any") {
    matchmeta <- matchmeta %>% filter(map_class == opts$mapclass)
}


matchmeta_slice <- pre_matchmeta %>%
    filter(
        start_dt >= opts$lower_dt,
        rating_min >= opts$lower_elo_slice,
        leaderboard_name == opts$leaderboard
    )

if (opts$mapclass != "Any") {
    matchmeta_slice <- matchmeta_slice %>% filter(map_class == opts$mapclass)
}
```


## Introduction

This document was built by filtering the data based on the following criteria:

- Leaderboard = **`r opts$leaderboard`**
- Matches started between **`r as.Date(opts$lower_dt)`** and **`r as.Date(max(matchmeta$start_dt))`**
- Matches have a map classification of "**`r opts$mapclass`**"
- The lowest Elo player in the match has an Elo greater than **`r opts$lower_elo`**
- Game length > 3 and < 180 in-game minutes

Please note that for the "Win rate by Elo" plot, all matches that have the
lowest Elo player in the match having an Elo greater **`r opts$lower_elo_slice`** have been included.

## Descriptives

### Matches Played by Patch

```{r, desc_patch}
plot_dist_patch(matchmeta)
```

### Matches Played by Map
```{r, desc_matches}
plot_dist_map(matchmeta)
```

### Matches Played by Game Length
```{r, desc_gamelength}
plot_dist_gamelength(matchmeta)
```

### Summary of Elo Distribution

```{r, desc_elo}
plot_dist_elo(matchmeta)
```


### Play Rate by Civilisation

```{r, desc_pr}
pr <- data_pr(matchmeta = matchmeta, players = players)
plot_pr(pr)
```




## Naive Win Rates

### Naive Win Rates by Civilisation

```{r, wr_naive}
wr_naive <- data_wr_naive(matchmeta = matchmeta, players = players)
plot_wr_naive(wr_naive)
```

### Naive Win Rates vs Play Rate

```{r, wr_naive_pr}
plot_pr_wr(wr_naive, pr)
```



## Averaged Win Rates

### Averaged Win Rates by Civilisation
```{r, wr_avg}
wr_avg_coef <- data_cvc(matchmeta = matchmeta, players = players)
wr_avg <- data_wr_avg(wr_avg_coef)
plot_wr_avg(wr_avg)
```

### Averaged Win Rates vs Play Rate

```{r, wr_avg_pr}
plot_pr_wr(wr_avg, pr)
```


## Miscellaneous Plots

### Naive Win Rates by Elo
```{r, wr_slice_elo, opts.label='square'}
plot_slice_elo(matchmeta = matchmeta_slice, players = players)
```

### Naive Win Rates by Game Length
```{r, wr_slice_gamelength, opts.label = 'square'}
plot_slice_gamelength(matchmeta = matchmeta, players = players)
```

### Civilisation v Civilisation Win Rates{.tabset .tabset-fade .tabset-pills}

```{r, wr_cvc, results = "asis"}
plots <- plot_cvc(wr_avg_coef)
id <- "cvcip"
cat(glue::glue('<label for="{id}">Select a Civilisation: </label>'))
cat(glue::glue('<input id="{id}">'))
for (civ in names(plots)) {
    display <- if_else(civ == "Aztecs", "true", "none")
    cat(glue::glue('<div class="{id}" id="{id}-{civ}" style="display:{display};">'))
    print(plots[[civ]])
    cat("</div>")
}
```


<br/>
<br/>